---
title: "Final Project Group 8"
author:
- affiliation: Department of Industrial and Systems Engineering, Auburn University
  name: 'Amir Mehdizadeh ^[Email: azm0127@auburn.edu </a>]'
- affiliation: Department of Industrial and Systems Engineering, Auburn University
  name: 'Jiafeng Ye ^[Email: jzy0087@auburn.edu </a>]'
- affiliation: Department of Psychological Sciences, Auburn University
  name: 'David Haste ^[Email: dah0048@auburn.edu </a>]'
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: show
    number_sections: no
    paged_df: yes
    theme: simplex
    toc: yes
    toc_float: yes
  includes:
    in_header: structure.tex
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FinalGroup8
This package can be downloaded through the use of the command
devtools::install_github(AU-R-Programming/Final-Project_Group-8/FinalGroup8)


Below is an example of using the my_lm function with an existing dataset. It provides information such as confidence intervals, beta, F-statistics, p-value, as well as graphs plotting the residuals, q-q plots, and histogram of residuals. 

```{r cars}
library(FinalGroup8)
df = read.csv("forestfires.csv")

X = df[,-1]
Y = df[,1]

my_lm(Y, X, 0.05)
```


Sources:
https://smac-group.github.io/ds/section-r-packages.html#section-basic-steps
http://rstudio-pubs-static.s3.amazonaws.com/159730_dc1df2f4cc0447fb866a0de3aeaa9117.html